---
title: "People in Surveys: Loudest Countries"
output: rmarkdown::github_document
---


```{r, message=FALSE}
library("tidyverse")
```



```{r}
cleaned_data <- data.table::fread("cleaned_data.csv")
```

### Intro

This is Part 2 of the series People in Surveys.

I am analysing data from a [survey](https://www.kaggle.com/kaggle/kaggle-survey-2018#multipleChoiceResponses.csv) conducted by Kaggle in October 2018, gathering data on the state of Machine Learning and Data Science as viewed from their subscribers.


## The state of ML and Data Science in LatAm

What is the distribution of the participants?

```{r}
cleaned_data %>% group_by(country) %>% count() %>% 
  ggplot(aes(reorder(country, -n), n)) + geom_col() +
  xlab("Countries") + ylab("") + ggtitle("Number of participants per country") +
  theme(aspect.ratio = 10/90) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  
```

The most active participants are people from the USA and India

```{r}
cleaned_data %>% filter(country %in% c('United States of America', "India")) %>% 
  group_by(country) %>% tally()
```
```{r}
4417/23859*100 + 4716/23859*100
```

Their participation is pretty much at pair. And together, they represent 38.28% of the voice in Data Science and ML in this survey.

If you are looking for further summary, here it is:
```{r}
cleaned_data %>% group_by(country) %>% count() %>% summary()
  
```
There is a 4386.8 difference between the 3rd quartile and the max value (which is the USA, leading India with just 299 more participants). This difference is almost as much as all the participants from India combined!

Their voice is more represented in this survey, and hence, these are the people who are influencing the [infographics](https://www.cloudfactory.com/hubfs/02-Contents/5-Infographics/Life-of-Data-Scientist-Infographic.pdf?hsCtaTracking=4ed5fb6f-cb6d-4b5f-971e-3f69697204c2%7C77b4ec9b-262d-4ae4-bab3-8ac3be56a4f8) and debates around the state of Data Science and Machine Learning.


Should the rest of the world's data scientist speak up? 
Do we differ? Do we recognise our practices with those of India and the USA?


Stay tunned for more.


